Proportional multi-state multiple-cohort life table model

### 2018-04-18 MSLT/MSLTdoc.Rmd
Checking different spline methods

assign(paste(sex, measure, "interpolated", sep = "_"), interpolated)
plot(interpolated$age,interpolated$rate)

  }
}

>>>>

assign(paste(sex, measure, "interpolated", sep = "_"), interpolated)
plot(interpolated$age,interpolated$rate)
 p <- ggplot(data = interpolated, aes(age,rate)) +
            geom_line(aes(color = "Interpolated")) 
            theme_classic()
            print(p)
  }
}
